A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-07-02 manuscript/CI_interactions.tex
some more Tomas comments

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information for the ecologist to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions. This uncertainty can, however, be constrained with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. By using an extremely well-sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions. 
    \item Overall, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies and the utility of treating interactions as probabilities in pinpointing areas where more study is needed. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE. This is 290 exactly.
\end{enumerate}

@@

    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. Even in extremely well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

@@

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks. We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S1}). By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data. When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).

@@

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S2} for details and a simple quantitative example).

@@

      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).

      The high spatiotemporal resolution and unusually high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information. A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand. If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S5}).

        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S7}).

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S8}). One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  Most pairs of species (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A). The bulk (92.24\%) of these co-occurring species pairs were never observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and was lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).

@@

  For most pairs of species $i$ and $j$, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S9}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively. Note that these are relatively large sample sizes compared to currently-available empirical networks~\citep{Morris2014}.

@@

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site. Interaction uncertainty means that some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
    Process uncertainty describes the fact that interactions occur with different probabilities during any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
    After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
    \end{center}
    \end{figure}

>>>>

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information for the ecologist to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using perhaps the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions. This uncertainty can, however, be constrained with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. By using a comprehensively sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions. 
    \item Overall, we demonstrate the utility of our approach, given the importance of acknowledging the uncertainty inherent in network studies, and the utility of treating interactions as probabilities in pinpointing areas where more study is needed. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE. This is 290 exactly.
\end{enumerate}

@@

    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

@@

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks. We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S2}). By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data. When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).

@@

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).

@@

      To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).

      The high spatiotemporal resolution and unusually high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).

@@

        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information. A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand. If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S6}).

        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S7} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S8}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S8}).

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}). One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  In the \emph{Salix}-based food webs sampled by~\citet{Kopelke2017}, most pairs of gallers and natural enemies (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A). The bulk (92.24\%) of these co-occurring species pairs were never observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and was lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).

@@

  For most pairs of species $i$ and $j$, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S9}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively. Note that these are relatively large sample sizes compared to currently-available empirical networks (e.g.,~\citealp{Morris2014}).

@@

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site. Interaction uncertainty means that some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
    \indent Process uncertainty describes the fact that interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
    \indent After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
    \end{center}
    \end{figure}

### 2018-07-02 manuscript/supplemental.tex
some more Tomas comments

\section*{Appendix S1: Mathematical framework}

@@

\section*{Appendix S2: Calculating uninformative and informative priors}

@@

\section*{Appendix S3: Details of \emph{Salix} data collection}

@@

\section*{Appendix S4: Results for \emph{Salix}-galler component}

@@

\section*{Appendix S5: Analyses using alternative prior}

@@

\section*{Appendix S6: Obtaining prior interaction probabilities}

@@

\section*{Appendix S7: R code for calculating posterior distributions and confidence intervals}

@@

\section*{Appendix S8: Simulating the effects of uncertainty on network structure}

  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty. We began by constructing 100 ``true" networks with 50 plant species, 50 galler species, and a connectance of 0.1. We ensured that each network had at least one link per plant and per galler. For each network, we calculated the mean number of links per plant, mean number of links per galler, and nestedness (NODF) as described in the main text. For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).

  Taking each ``true" network as a starting point, we then applied process uncertainty. The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution. As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred. The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive. The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$. If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network. As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network. For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.

  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks. As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution. We also randomly selected the probability, $p$, of detecting each interaction. To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10. We created 100 detection-filtered networks for each process-filtered network (10000 per true network). For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF. Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.

  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs). The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests). The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types. Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001). We note that these tests may reflect the large number of detection-filtered webs generated by our simulation. A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network. This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.

  Note that this simulation uses several simplifying assumptions. For instance, we treat interactions as independent and ignore the possibility for, for example, competition between gallers. A thorough exploration of the effects of interaction contingency, different distributions of co-occurrences, etc. would be an interesting topic for future work but is beyond the scope of the current study. We also neglect interaction uncertainty in this example. Interaction uncertainty could be included by, for example, modelling interactions between individuals of each species. In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate. Very small or very large individuals might not participate in some interactions that are feasible for most members of the species.

  \begin{figure}
  \label{sim_props}
  \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1. For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling. For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction. For each network, we show the mean (+/- SD) connectance, links per plant, nestedness (NODF), and links per galler.}
  \begin{center}
  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
  \end{center}
  \end{figure}

>>>>

\section*{Appendix S1: Simulating the effects of uncertainty on network structure}

  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty. We began by constructing 100 ``true" networks with 50 consumer species, 50 resource species, and a connectance of 0.1. We ensured that each network had at least one link per consumer and per resource. For each network, we calculated the mean number of links per consumer, mean number of links per resource, and nestedness (NODF) as described in the main text. For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).

  Taking each ``true" network as a starting point, we then applied process uncertainty. The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution. As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred. The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive. The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$. If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network. As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network. For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF.

  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks. As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution. We also randomly selected the probability, $p$, of detecting each interaction. To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10. We created 100 detection-filtered networks for each process-filtered network (10000 per true network). For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF. Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.

  With each additional layer of uncertainty, the number of consumers and resources included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs). The connectance and number of links per consumer and per resource decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests). The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types. Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001). We note that these tests may reflect the large number of detection-filtered webs generated by our simulation. A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network. This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.

  Note that this simulation uses several simplifying assumptions. For instance, we treat interactions as independent and ignore the possibility for, for example, competition between resources. A thorough exploration of the effects of interaction contingency, different distributions of co-occurrences, etc. would be an interesting topic for future work but is beyond the scope of the current study. We also neglect interaction uncertainty in this example. Interaction uncertainty could be included by, for example, modelling interactions between individuals of each species. In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate. Very small or very large individuals might not participate in some interactions that are feasible for most members of the species.

  \begin{figure}
  \label{sim_props}
  \caption{We created 100 random networks containing 50 consumers and 50 resources, with a connectance of 0.1. For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling. For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction. For each network, we show the mean (+/- SD) connectance, links per consumer, nestedness (NODF), and links per resource.}
  \begin{center}
  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
  \end{center}
  \end{figure}

\section*{Appendix S2: Mathematical framework}

@@

\section*{Appendix S3: Calculating uninformative and informative priors}

@@

\section*{Appendix S4: Details of \emph{Salix} data collection}

@@

\section*{Appendix S5: Results for \emph{Salix}-galler component}

@@

\section*{Appendix S6: Analyses using alternative prior}

@@

\section*{Appendix S7: Obtaining prior interaction probabilities}

@@

\section*{Appendix S8: R code for calculating posterior distributions and confidence intervals}

@@
